\clearpage
\section{Appendix A}

\subsection{Team Management}

\subsubsection{Justification of the Division of Labour}

The four major cells were divided between the team as recommended in the specification.
It was decided to also attempt the optional cells for teams of four.
An extra person in a team of five would be in charge of designing the halfadder and xor2.
The halfadder was assigned to the team member designing the fulladder as their expertise was greater for designing adder cells.
The xor2 cell was assigned to the team member designing the rdtype as this cell was assumed less time consuming than the two other sets of major cells.
The remaining cells were grouped and divided among the teams as shown in Table~\ref{tab:cells}.

\begin{table}[h]
   \centering
    \begin{tabular}{| p{4.5cm} | p{6.5cm} |}
    \hline
      \textbf{Cell Groupings} & \textbf{Reasoning}\\ \hline
      and2, and2, nand3, nand4  &	Nands and Ands are similar in design.\\ \hline
      buffer, trisbuf  &	Buffers are similar in design.\\ \hline
      inverter, nor2, nor3, or2   &	 Nors and Ors similar in design. Inverter is a simple cell assigned to distribute load.\\ \hline
      rowcrosswer, tiehigh, tielow &	Low complexity cells assigned to team member tasked with designing both adders.\\ \hline
    \end{tabular}
    \caption{Cell design groupings and reasoning}
    \label{tab:cells}
\end{table}

\subsubsection{Version Control}
The Git revision control system was used throughout the project to facilitate collaborative working.
GitHub is a web-based hosting service for git. 
This was used to share files, allocate work and track bugs.

\subsubsection{Process automation}
The team produced a number of scripts to improve productivity by automating processes such extraction from magic, design simulation and consistency checking.
Using \LaTeX allowed the databook compilation to also be automated as separate files for each cell were stored in the hierarchy of folders.   
This way each designer could add their own files to the data book independently.



\clearpage
\subsection{Division of Labour}
